### 2019-05-07 styles/texmf/tex/latex/Reply_to_reviewer_template.tex
Update presentation

\documentclass[a4paper,11pt]{article}              %  final version

\usepackage{graphics}
\usepackage{fancyhdr}
\usepackage{amssymb,amsfonts,amsmath,amsthm}
\usepackage{natbib}
\usepackage{bstnotations}
\usepackage[margin=30mm]{geometry}
%\geometry{left=2cm,right=2cm,top=3cm,bottom=3cm}

\usepackage{colortbl}
\usepackage{tikz}
\usepackage{subfigure}

\usepackage{authblk}
\renewcommand\Affilfont{\itshape\small}

\newcommand{\revcomment}[1]{
  \begin{quotation}
    {\small
   \noindent   \textbf{Comment:}
   \em #1
    }    
  \end{quotation}
}

\newcommand{\reply}[1]
{
 \noindent   \textbf{Reply:}
#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                  DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Reply to reviewers\\
	journal\_paper\_ID\\
	\textbf{title}}

\author[1]{A. Author} \author[1]{B. Author}

\affil[1]{Chair of Risk, Safety and Uncertainty Quantification, ETH
  Zurich, Stefano-Franscini-Platz 5, 8093 Zurich, Switzerland}

\date{}
\maketitle

The authors would like to thank the reviewers for their thorough reading
of the manuscript and their constructive comments. Corrections have been
made accordingly and are highlighted in red in the revised version of
the paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reply to reviewer \# 1}
%	\revcomment{The papers fails to cite some published papers that used
%	  enhanced Kriging methods for RBDO. The authors should do better
%	  literature survey.}
%	
%	\reply{In the revised version of the paper, some recent references have
%	  been added such as ...}

\revcomment{Cut/paste from the review each comment}

\reply{when writing a rebuttal, follow the golden rule ``always agree
  with the reviewer (to the largest possible extent), and change as
  little as possible in the paper.''}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reply to reviewer \# 2}
\revcomment{The papers fails to cite some published papers that used
  enhanced Kriging methods for RBDO. The authors should do better
  literature survey.}

\reply{In the revised version of the paper, some recent references have
  been added such as ...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reply to editor}
If anything to be added in this section

%%%%%%%%%%%%%%%%%%%%%%% ADDITIONAL REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% References with bibTeX database:
% e.g.
\nocite{SudretHDR}

\renewcommand{\refname}{Additional references}
\small
\bibliographystyle{chicago}
\bibliography{biblioRSUQ}
\end{document}

### 2019-05-07 latex/BeamerGPR.tex
Update presentation

\documentclass[]{rsuqbeamernew}

\title[Notes on GPR]{Notes on Gaussian Process Regression (GPR)}

\author[D. Wicaksono]{Damar Wicaksono}
\institute[RSUQ, ETH Z\"urich]{Chair of Risk, Safety and Uncertainty 
Quantification -- ETH Z\"urich}

\date[28.03.2019]

\graphicspath{{Figures/}}
\usepackage{caption}
\usepackage{listings}
\usepackage{tikz}
\usepackage{pifont}
%\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

%% Note: the title page will be created automatically

\begin{document}

%===============================================================================
\begin{frame}{Outline}

\tableofcontents

\end{frame}
%===============================================================================

\section{UQLab Users}

%===============================================================================
\begin{frame}{UQLab users}

Ideas for our UQ community are initiated
from our understanding of the \emph{natural} audience, \textbf{UQLab users}:

\begin{itemize}
  \item Since its public release in 2015, UQLab users has almost reached 2'000 users from 77 countries,
  with over 60 unique active users per day and up to 130 weekly.
  \item We ask users to register, but beyond users affiliation,
  we don't know much about them or how they are using UQLab\footnote{Which are not the point of registration. For the actual reasons on why registration is required, see Stefano's blog on \emph{Why do we ask you to register to get UQLab? Why does the "core" folder contain obscured files?}}.
\end{itemize}

How can we know more of our audience up to the present?

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}{UQLab users: A glimpse from support emails}

  Many are about registration, license, and installations:
  \begin{itemize}
    \item From:$\blacksquare@\blacksquare$.fr, Subject: Loose the licence file
    \begin{quotation}
     I'm PhD candidate and I want to use your UQlab toolbox but I loose my licence email and I can't find it on my computer.
    \end{quotation}
  \item From:$\blacksquare@\blacksquare$.com, Subject: Registration, captcha
  \begin{quotation}
  Trying to register for downloading UQLab, I always fail to find the captcha. Could you please check it? I'd be surprised to find out that I am a bot :)
\end{quotation}
\item From:$\blacksquare.\blacksquare@\blacksquare$.edu, Subject: problem while installing uqlab
\begin{quotation}
  i have problems installing on MATLAB 2010b, the version 2014a seems to work ok. i just want to let you know about that. 
\end{quotation}
\end{itemize}
\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}{UQLab users: A glimpse from support emails}

  Some are technical questions about UQLab:
  \begin{itemize}
    \item From:$\blacksquare@\blacksquare$.edu.au, Subject: sequential design strategy
    \begin{quotation}
      However I was wondering if there is a way to set up sequential design strategy in UQlab. 
    \end{quotation}
    \item From: many, Subject: Problem with running UQlab
    \begin{quotation}
      I am running this piece of code:
      ....
      and am seeing this error message:
      ....
      I was wondering if you had any suggestions to resolving this problem.
    \end{quotation}
  \end{itemize}

  Some are technical questions about UQ in practice (and in context):
  \begin{itemize}
      \item From:$\blacksquare@\blacksquare$.ch, Subject: Best case and worst case during uncertainity quantification
      \begin{quotation}
      Lately our group is trying to use Monte Carlo approach to quantify uncertainty in our estimation of human optimum walking performance. Particularly, we require some knowledge on defining the best and worst case scenarios. Can you guide us ? 
    \end{quotation}
  \end{itemize}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}{UQLab users: A glimpse from support emails}

Some are nice,
\begin{itemize}
  \item From: david.$\blacksquare@\blacksquare$.de, Subject: Citing UQLab
  \begin{quotation}
    As I won't have the chance to employ it in my work, \textbf{I would like to include it in my literature section to raise awareness for students after me}. Unfortunately, I couldn't find how to cite UQLab. Any recommendations?
  \end{quotation}
  \item From: $\blacksquare@\blacksquare$.pt, Subject: credits in publications
  \begin{quotation}
    I haven't started to use UQlab yet but at a glance let me tell you that it seems a very nice job!
  \end{quotation}
\end{itemize}

Some can be nicer...
\begin{itemize}
  \item From:$\blacksquare@\blacksquare$.com, Subject: CV as a parameter estimation method
  \begin{quotation}
    Hey, 
    I would like to ask where I can find more explanation about how cross validation is used in estimating parameters of kriging models. The manuel didn't help much. 
  \end{quotation}
  \item From:$\blacksquare@\blacksquare$.edu, Subject: Unregister
  \begin{quotation}
    Kindly cancel my registration!

    Thank you!
  \end{quotation}
\end{itemize}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQLab users: A glimpse from external citations}

\begin{columns}
    \column{0.5\textwidth}
  \begin{minipage}[c][0.30\textheight][c]{\linewidth}
    \begin{figure}
      \centering
      \includegraphics[width=0.8\linewidth]{../figures/cit_stat}
    \end{figure}
  \end{minipage}
  \begin{minipage}[c][0.6\textheight][c]{\linewidth}
    \begin{figure}
      \centering
      \includegraphics[width=0.75\linewidth]{../figures/uqlab_citations}
    \end{figure}
  \end{minipage}

  \column{0.5\textwidth}
    \begin{itemize}
    \item Between 2016--2019, about 83 papers are published in which UQLab is used as an analysis tool.
    \item \emph{Engineering applications} is the majority.
  \end{itemize}
  \begin{minipage}{\linewidth}
    \begin{tabularx}{\textwidth}{Xc}
      \hline
      \scriptsize{Fields of Applications} & \footnotesize{Number of Citations} \\
      \hline
      \footnotesize{Electrical} & 19  \\
      \footnotesize{Civil} & 11 \\
      \footnotesize{Chemical} & 7 \\
      \footnotesize{Mechanical} & 6 \\
      \footnotesize{Remote sensing} & 5 \\
      \footnotesize{Nuclear} & 5 \\
      \footnotesize{Ocean} & 4 \\
      \footnotesize{Energy} & 1 \\
      \hline
    \end{tabularx}
  \end{minipage}%
  \hfill
\end{columns}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQLab users: Some can be very productive}

Some authors are able to produce multiple papers using UQLab as part of their analysis.
For example:

  \begin{thebibliography}{Dijkstra, 1982}
    \footnotesize{
    \bibitem[Xie and Schenkendorf, 2019]{Xie2019}
    Xiangzhong Xie and Ren\'e Schenkendorf
    \newblock Stochastic back-off-based robust process design for continuous crystallization of ibuprofen, {\em Computers and Chemical Engineering}, vol. 124, 2019.

    \bibitem[Xie et al., 2018]{Xie2018}
    Xiangzhong Xie, R\"udiger Ohs, A. C. Spiess, Ulrike Krewer, and Ren\'e Schenkendorf,
    \newblock Moment-independent sensitivity analysis of enzyme-catalyzed reactions with correlated model parameters, {\em IFAC-PapersOnLine}, vol. 51, 2018.

    \bibitem[Emenike, 2017]{Emenike2018}
    V. N. Emenike, Xiangzhong Xie, Ren\'e Schenkendorf, A. C. Spiess, and Ulrike Krewer,
    \newblock Robust dynamic optimization of enzyme-catalized carboligation: a point estimate-based back-off approach, {\em Computers and Chemical Engineering}, 2018.

    \bibitem[Schenkendorf et al., 2017]{Schenkendorf2017}
    Ren\'e Schenkendorf, Xiangzhong Xie, and Ulrike Krewer
    \newblock An efficient polynomial chaos expansion strategy for active fault identification of chemical processes, {\em Computer Aided Chemical Engineering}, 2017.

    \bibitem[Xie et al., 2017]{Xie2017}
    Xiangzhong Xie, Ren\'e Schenkendorf, and Ulrike Krewer,
    \newblock Robust design of chemical processes based on a one-shot sparse polynomial chaos expansion concept, {\em Computer Aided Chemical Engineering}, 2017.}
  \end{thebibliography}
% Note that there are other cases
\end{frame}
%===============================================================================

\section{Ideas for an Online Community}

%===============================================================================
\begin{frame}[t]{Ideas for an Online Community}

\end{frame}
%===============================================================================

\section{Tools for an Online Community}

\section{UQWorld}

%===============================================================================
\begin{frame}[t]{Introducing UQWorld}

  \begin{columns}
    \column{0.35\textwidth}
    \begin{minipage}[c][0.85\textheight][c]{\linewidth}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\linewidth]{../figures/uqworld_logo.png}
      \end{figure}
    \end{minipage}

    \column{0.65\textwidth}
    \begin{itemize}
      \item Between 2016--2019, about 83 papers are published in which UQLab is used as an analysis tool.
      \item already live at \texttt{uqworld.org}
    \end{itemize}
    \hfill
  \end{columns}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQWorld: Structure and organization}

\texttt{UQWorld} is organized into three main categories:
\begin{columns}
  \column{0.3\textwidth}
  \begin{figure}
    \includegraphics[width=0.70\textwidth]{../figures/all-about-uq_512}
    \caption*{All About UQ}
  \end{figure}

  \column{0.3\textwidth}
  \begin{figure}
    \includegraphics[width=0.65\textwidth]{../figures/uq-resources_512}
    \caption*{UQ Resources}
  \end{figure}

  \column{0.3\textwidth}
  \begin{figure}
    \includegraphics[width=0.6\textwidth]{../figures/uq_with_uqlab_512}
    \caption*{UQ with UQLab}
  \end{figure}
\end{columns}

\begin{itemize}
  \item \emph{All About UQ} contains the free UQ discussion forum and the Chair's published post (\textbf{UQ-centered} space).
  \item \emph{UQ Resources} contains news, updates, case studies, and other resources from UQ community at large (\textbf{UQ-centered} space).
  \item \emph{UQ with UQLab} is the corner for UQLab users, a place to get help with UQLab, as well as updates from the Developer Team (\textbf{UQLab-centered} space).
\end{itemize}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQWorld: An Applied UQ Community}

The largest chunk of space in \texttt{UQWorld} caters to UQ practitioners---from the uninitiated to skilled---regardless the software tool they are using:

\begin{itemize}
  \item \emph{UQ Discussion Forum}: A lightly-moderated forum to ask, discuss, and share (Examples: Introduce projects and UQ methods applied, )
  \item \emph{Chair's Blog} (Example: Bruno's posts on \emph{Getting started with UQ} and \emph{How to define my probabilistic input distributions?}).
  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
  \item \emph{Case studies} (Example: Paul's post on the calibration of heat transfer model).
  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
\end{itemize}

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQWorld: The UQLab User Community}

\texttt{UQWorld} is the definitive UQLab user community:

\end{frame}
%===============================================================================

%===============================================================================
\begin{frame}[t]{UQWorld: Structure and organization}

Member write access to categories within \texttt{UQWorld} is controlled;
In some categories, members can't start their own topic.
This is how the Chair maintains the \emph{editorial content} of \texttt{UQWorld}.

\begin{tabularx}{\textwidth}{Xccc}
  \hline
  Sub-categories                            & Public     & RSUQ       &  RSUQ-Prime\\
  \hline
  \footnotesize{Chair's Blog}               & \ding{55}  & \ding{55}  & \checkmark \\
  \footnotesize{FAQ}                        & \ding{55}  & \ding{55}  & \checkmark \\
  \footnotesize{Developers Corner}          & \ding{55}  & PA         & \checkmark \\
  \footnotesize{Future/Draft}               & \ding{55}  & \checkmark & \checkmark \\
  \footnotesize{News and Announcements}     & \ding{55}  & \checkmark & \checkmark \\
  \footnotesize{Benchmarks}                 & PA         & \checkmark & \checkmark \\
  \footnotesize{Case Studies}               & \checkmark & \checkmark & \checkmark \\
  \footnotesize{Community Q\&A and How To}  & \checkmark & \checkmark & \checkmark \\   
  \footnotesize{Features Requests}          & \checkmark & \checkmark & \checkmark \\
  \footnotesize{UQWorld Community (Meta)}   & \checkmark & \checkmark & \checkmark \\
  \footnotesize{UQ Discussion Forum}        & \checkmark & \checkmark & \checkmark \\
  \hline
\end{tabularx}

\end{frame}
%===============================================================================

\section{Demo}

\section{What's next}

%===============================================================================
\begin{frame}[t]{UQWorld: What's next}

\end{frame}
%===============================================================================

\end{document}

### 2019-05-07 styles/texmf/tex/latex/MascotNum/MascotNumTemplate.tex
Update presentation

% % % % % % % % % % % % % % % % % % % % % % % % % % % %
% Template file for MascotNum 2014 Phd Student papers 
% November 4th, 2013
% (c) Stefano Marelli, Bruno Sudret
% Chair of Risk, Safety, and Uncertainty Quantification 
% ETH Zürich
% 
% % % % % % % % % % % % % % % % % % % % % % % % % % % %
\documentclass{MascotNumAbstract}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % Beginning of the personal information section % % %
% % % PLEASE NOTE: All of the fields are mandatory! % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % %

% Authors names, in the form 'initials surname', as in:
% J. Smith
 \author{A. PhDStudent}
% Short form of the author names (will appear in the odd/even pages of the abstracts)
 \shortauthor{PhDStudent} 
% Corresponding author
 \correspondingauthor{A. PhDStudent}
% Corresponding author address
 \firstauthoraddress{\emph{Chair of Risk, Safety and Uncertainty Quantification}, ETH Z\"urich, Wolfgang-Pauli-strasse 15, CH-8093 Z\"urich, Switzerland}
% University where the MSc was acquired
 \masteruniversity{University where the master's degree was completed}
% Current university (PhD)
 \phduniversity{University where the Ph.D is prepared}
% Expected phd duration. Format:
 \phdtime{2012-2015}
% Supervisors and affiliations  
 \supervisors{Prof. Supervisor1 (University1) and Prof. Supervisor2
   (University2) and Dr. Supervisor3 (Company)}
% Webpage of the author or of the university group
 \webaddress{http://www.ibk.ethz.ch/su/index_EN}
% Contact mail
 \contactmail{marelli@ibk.baug.ethz.ch}

% Title of the abstract
 \title{MascotNum2014 conference - Template abstract for the PhD papers} 
% short version of the title for the running headers
 \shorttitle{Short title for the abstract}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % %   End of the personal information section 	% % %
% PLEASE NOTE: All of the fields are mandatory!     % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % %

% full abstract text
  \begin{document}

  Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus
  elit, vestibulum ut, placerat ac, adipiscing vitae, felis. Curabitur
  dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id,
  vulputate a, magna. Donec vehicula augue eu neque. Pellentesque
  habitant morbi tristique senectus et netus et malesuada fames ac
  turpis egestas. Mauris ut leo. Cras viverra metus rhoncus sem. Nulla
  et lectus vestibulum urna fringilla ultrices.  Phasellus eu tellus sit
  amet tortor gravida placerat. Integersapien est, iaculis in, pretium
  quis, viverra ac, nunc. Praesent eget sem vel leo ultrices bibendum.
  Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis
  ac, nulla.  Curabitur auctor semper nulla. Donec varius orci eget
  risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis,
  diam. Duis eget orci sit amet orci dignissim rutrum.

  Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi.
  Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis
  vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan biben-
  dum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac
  orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante.
  Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis
  parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna.
  Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus
  mauris.

  Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat
  at, tincidunt tristique, libero. Vivamus viverra fermentum felis.
  Donec nonummy pellentesque ante. Phasellus adipiscing semper elit.
  Proin fermentum massa ac quam. Sed diam turpis, molestie vitae,
  placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula,
  eleifend at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula
  feugiat magna. Nunc eleifend consequat lorem. Sed lacinia nulla vitae
  enim. Pellentesque tincidunt purus vel magna.  Integer non enim.
  Praesent euismod nunc eu purus. Donec bibendum quam in tellus.  Nullam
  cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim.
  Vestibulum pellentesque felis eu massa.

  Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae
  lacus tincidunt ultrices. Lorem ipsum dolor sit amet, consectetuer
  adipiscing elit. In hac habitasse platea dictumst. Integer tempus
  convallis augue. Etiam facilisis.  Nunc elementum fermentum wisi.
  Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis
  odio placerat quam, ac pulvinar elit purus eget enim. Nunc vitae
  tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor vitae
  risus porta vehicula.

  Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a
  faucibus semper, leo velit ultricies tellus, ac venenatis arcu wisi
  vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis
  posuere, turpis lacus congue quam, in hendrerit risus eros eget felis.
  Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor.
  Nulla facilisi. Sed a turpis eu lacus commodo facilisis. Morbi
  fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
  vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis
  cursus enim ut augue. Cras ac magna. Cras nulla. Nulla egestas.
  Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel
  est.  Curabitur consectetuer.

  Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit
  amet, laoreet vitae, arcu. Aenean faucibus pede eu ante. Praesent enim
  elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros,
  malesuada sit amet, fermentum eu, sodales cursus, magna. Donec eu
  purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas
  dui, et convallis elit erat sed nulla. Donec luctus. Curabitur et
  nunc.  Aliquam dolor odio, commodo pretium, ultricies non, pharetra
  in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas
  vel, odio.

  Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio.
  Sed vehicula hendrerit sem. Duis non odio. Morbi ut dui. Sed accumsan
  risus eget odio. In hac habitasse platea dictumst. Pellentesque non
  elit. Fusce sed justo eu urna porta tincidunt. Mauris felis odio,
  sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
  pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis
  congue purus metus ultricies tellus. Proin et quam. Class aptent
  taciti sociosqu ad litora torquent per conubia nostra, per inceptos
  hymenaeos. Praesent sapien turpis, fermentum vel, eleifend faucibus,
  vehicula eu, lacus.

% Short biography
  \vfill

  {\bf Short biography --}~~ Each PhD student is asked to present in
  max. 5 lines his/her background and the context of the PhD thesis, the
  sources of funding, links with industry, etc.

\vspace*{1cm}

\end{document}

### 2019-05-07 styles/texmf/tex/latex/ethminutes/template-minutes.tex
Update presentation

\documentclass[11pt,A4]{article}

%\usepackage{charter}
%\usepackage[charter]{mathdesign}
\usepackage{ethminutes}
\usepackage{bstnotations}
\usepackage{tikz}

%\usepackage[english]{babel}
\selectlanguage{english}
\graphicspath{{./},{./Figures/}}
\renewcommand{\baselinestretch}{1.3}

\begin{document}
%---------------------------------------------------------------------
%     Properties of the document
%--------------------------------------------------------------------- 
\RefDocument{Thesis-Name-001}
\Date{March 11th, 2013}
\LieuReunion{UQ Chair}
\Redacteur{Ph.D student}     
\TitleReport{Ph.D thesis progress meeting}
\DateDiffusion{--} 
\Destinataires{B. Sudret}

\entete
\pieddepage 
\PageDeGarde

\vspace*{2em}

%%% Actions
 \begin{table}[!ht]
    \centering
 \begin{tabularx}{\textwidth}{>{\lratio{0.3}\raggedright\arraybackslash}Y
      >{\lratio{1}\raggedright\arraybackslash}Y   >{\lratio{0.2}}Y}

      \begin{tikzpicture} 
        \draw (0,0) node[fill=black!10!white, draw=black, rectangle, text
        centered, rounded corners = 3pt,inner sep= 5pt] (Participants)
        {\bf Actions};
      \end{tikzpicture} \\[-0.3em] \toprule {\bf Responsable} & {\bf
        Action} & {\bf Deadline} \\\hline 
    Your Name & Description of the action& dd/mm/year\\ \bottomrule
    \end{tabularx}
  \end{table}

\newpage

%---------------------------------------------------------------------
%     Main text
%---------------------------------------------------------------------

\section{First section}
\subsection{Subsection}
\subsubsection{Subsubsection}

TARATATA

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed non risus.
Suspendisse lectus tortor, dignissim sit amet, adipiscing nec, ultricies

sed, dolor. Cras elementum ultrices diam. Maecenas ligula massa, varius
a, semper congue, euismod non, mi. Proin porttitor, orci nec nonummy
molestie, enim est eleifend mi, non fermentum diam nisl sit amet erat.
Duis semper. Duis arcu massa, scelerisque vitae, consequat in, pretium
a, enim. Pellentesque congue. Ut in risus volutpat libero pharetra
tempor. Cras vestibulum bibendum augue. Praesent egestas leo in pede.
Praesent blandit odio eu enim. Pellentesque sed dui ut augue blandit
sodales. Vestibulum ante ipsum primis in faucibus orci luctus et
ultrices posuere cubilia Curae; Aliquam nibh. Mauris ac mauris sed pede
pellentesque fermentum. Maecenas adipiscing ante non diam sodales
hendrerit. Ut velit mauris, egestas sed, gravida nec, ornare ut, mi.
Aenean ut orci vel massa suscipit pulvinar. Nulla sollicitudin. Fusce
varius.

\begin{equation}
  \label{eq:001}
  E = mc^2
\end{equation}

Ligula non tempus aliquam, nunc turpis ullamcorper nibh, in
tempus sapien eros vitae ligula. Pellentesque rhoncus nunc et augue.
Integer id felis. Curabitur aliquet pellentesque diam. Integer quis
metus vitae elit lobortis egestas. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Morbi vel erat non mauris convallis
vehicula. Nulla et sapien. Integer tortor tellus, aliquam faucibus,
convallis id, congue eu, quam. Mauris ullamcorper felis vitae erat.
Proin feugiat, augue non elementum posuere, metus purus iaculis lectus,
et tristique ligula justo vitae magna. Aliquam convallis sollicitudin
purus. Praesent aliquam, enim at fermentum mollis, ligula massa
adipiscing nisl, ac euismod nibh nisl eu lectus. Fusce vulputate sem at
sapien. Vivamus leo. Aliquam euismod libero eu enim. Nulla nec felis sed
leo placerat imperdiet. Aenean suscipit nulla in justo. Suspendisse
cursus rutrum augue. Nulla tincidunt tincidunt mi. Curabitur iaculis,
lorem vel rhoncus faucibus, felis magna fermentum augue, et ultricies
lacus lorem varius purus. Curabitur eu amet.

%%%
\subsection{Table}
This is a sample table referred to as Table~\ref{tab:001}.

\begin{table}[!ht]
  \begin{center}      \caption{Exemple de table} \label{tab:001}
    \begin{tabularx}{\textwidth}
      {>{\lratio{0.9}}Y>{\lratio{0.9}}Y>{\lratio{0.9}}Y>{\lratio{1.3}}Y}
      \hline \rowcolor[gray]{0.98} {Parameter} & {Distribution} & {Mean} &
      {Coefficient of variation} \\ \hline
      {$L$}		& {Lognormal}		& {$1$ m}		& {$3\%$}		\\
      {$b$}		& {Lognormal}		& {$10$ cm}		& {$3\%$}		\\
      {$h$}		& {Lognormal}		& {$1$ cm}		& {$3\%$}		\\
      {$F$}		& {Lognormal}		& {$200$ N}		& {$20\%$}		\\
      {$E_f$}		& {Lognormal}		& {$300$ GPa}		& {$15\%$}		\\
      {$E_m$}		& {Lognormal}		& {$10$ GPa}		& {$15\%$}		\\
      {$\rho_f$}	& {Lognormal}		& {$1800$ kgm$^{-3}$}	& {$3\%$}		\\
      {$\rho_m$}	& {Lognormal}		& {$1200$ kgm$^{-3}$}	& {$3\%$}		\\
      {$f$} & {Lognormal} & {$0.5$} & {$10\%$} \\ \hline
    \end{tabularx}
  \end{center}
\end{table}

%%% 
\subsection{Figure}
This is a sample figure referred to as Figure~\ref{fig:001}.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=3cm]{Dummy}
  \caption{Title} \label{fig:001}
\end{figure}

%%% 
\subsection{Notation}
A set of standard notation is defined in the file
\texttt{bstnotations.sty} and shall be used whenever justified.

%%%
\subsection{References}
Citations are managed with \textsc{Bib}\TeX. A data base (\eg
\texttt{biblioUQ.bib}) is used to gather all the bibliography. All
papers of interest for the PhD shall be stored in this
\texttt{bib}-file. JabRef is a good Java-based reference manager that
works under all operating systems and allows a simple management of the references.

In order to use it, the commands \texttt{$\backslash$citep} and
\texttt{$\backslash$citet} from the \texttt{natbib} package are used:
\begin{itemize}
\item If the citation appears {\em within} a sentence, it is referred to
  using \texttt{$\backslash$citet}, as in: 
  \begin{quotation}
    \citet{Bourinet2011} introduced support vector machines and subset
    simulation in order to compute small probabilities of failure.
  \end{quotation}
\item If the citation appears {\em at the end} of the sentence, \ie
  using parenthesis, the \texttt{$\backslash$citep} command shall be
  used, as in:
  \begin{quotation}
    The use of support vector machines for structural reliability
    analysis was proposed recently
    \citep{Basudhar2008a,Basudhar2008b,Bourinet2011}.
  \end{quotation}
\end{itemize}

% References
\renewcommand{\bibname}{References}
\bibliographystyle{chicago}
\bibliography{biblioUQ}

\label{end}
\end{document}

### 2019-05-07 styles/texmf/tex/latex/rsuqposter/rsuqposterA0_template.tex
Update presentation

\documentclass{rsuqposterA0}

\author{Ann Author}
\title{A0 Poster template}

\usepackage[framemethod=tikz]{mdframed}
\usepackage{lipsum}

\usepackage{tcolorbox}
\definecolor{mycolor}{rgb}{0.122, 0.435, 0.698}

\newmdenv[innerlinewidth=1pt, roundcorner=1cm,linecolor=mycolor,innerleftmargin=.5cm,
innerrightmargin=.5cm,innertopmargin=6pt,innerbottommargin=6pt]{mybox}

\begin{document}
{	\VERYHuge
some content
}

\colorbox{rsuqlightblue}{
	\begin{minipage}[t][13cm][c]{20cm}
		even bigger
	\end{minipage}
}\hfill
\colorbox{ETH1}{
	\parbox[t][13cm][c]{35cm}{
		this is funny
	}
}
\begin{tcolorbox}[colback=white!5!white,colframe=blue!75!black,title=My nice heading]
\parbox{.3\textwidth}{	This is another \textbf{tcolorbox}}
\end{tcolorbox}

% finally put the footer at the end of the document
\rsuqfooter{}
\end{document}

### 2019-05-07 styles/texmf/tex/latex/rsuqpreprint/DummyPaper.tex
Update presentation

--- 2019-05-07 styles/texmf/tex/latex/ethminutes/template-minutes.tex
@@
-\documentclass[11pt,A4]{article}
+\documentclass[11pt]{article}
 
-%\usepackage{charter}
-%\usepackage[charter]{mathdesign}
-\usepackage{ethminutes}
+\usepackage[margin=25mm]{geometry}
+%\geometry{left=2cm,right=2cm,top=3cm,bottom=3cm}
+\usepackage{graphics}
+\usepackage{colortbl}
+\usepackage{subfigure}
+\renewcommand*\thesubfigure{(\Alph{subfigure})} 
+\usepackage{fancyhdr}
+\usepackage{amssymb,amsfonts,amsmath,amsthm}
+\usepackage{natbib}
 \usepackage{bstnotations}
-\usepackage{tikz}
 
-%\usepackage[english]{babel}
-\selectlanguage{english}
+\usepackage{authblk}
+\renewcommand\Affilfont{\itshape\small}	
+\parindent 0em
+\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
+
+%
+\renewcommand{\baselinestretch}{1.5}
 \graphicspath{{./},{./Figures/}}
-\renewcommand{\baselinestretch}{1.3}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                  DOCUMENT
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-%---------------------------------------------------------------------
-%     Properties of the document
-%--------------------------------------------------------------------- 
-\RefDocument{Thesis-Name-001}
-\Date{March 11th, 2013}
-\LieuReunion{UQ Chair}
-\Redacteur{Ph.D student}     
-\TitleReport{Ph.D thesis progress meeting}
-\DateDiffusion{--} 
-\Destinataires{B. Sudret}
+\title{The Title of an Incredibly Innovative Paper}
 
-\entete
-\pieddepage 
-\PageDeGarde
+\author[1]{A. Author1} \author[1]{B. Author2} \author[2]{C. Author3}
 
-\vspace*{2em}
+\affil[1]{Chair of Risk, Safety and Uncertainty Quantification,
 
-%%% Actions
- \begin{table}[!ht]
-    \centering
- \begin{tabularx}{\textwidth}{>{\lratio{0.3}\raggedright\arraybackslash}Y
-      >{\lratio{1}\raggedright\arraybackslash}Y   >{\lratio{0.2}}Y}
+  ETH Zurich, Stefano-Franscini-Platz 5, 8093 Zurich, Switzerland}
 
-      \begin{tikzpicture} 
-        \draw (0,0) node[fill=black!10!white, draw=black, rectangle, text
-        centered, rounded corners = 3pt,inner sep= 5pt] (Participants)
-        {\bf Actions};
-      \end{tikzpicture} \\[-0.3em] \toprule {\bf Responsable} & {\bf
-        Action} & {\bf Deadline} \\\hline 
-    Your Name & Description of the action& dd/mm/year\\ \bottomrule
-    \end{tabularx}
-  \end{table}
+\affil[2]{Another Lab, Another University, Address, Country}
 
-\newpage
+\date{}
+\maketitle
 
-%---------------------------------------------------------------------
-%     Main text
-%---------------------------------------------------------------------
+\abstract{This is the abstract -- This is the abstract This is the
+  abstract This is the abstract This is the abstract This is the
+  abstract This is the abstract This is the abstract This is the
+  abstract This is the abstract This is the abstract This is the
+  abstract This is the abstract This is the abstract This is the
+  abstract This is the abstract This is the abstract This is the
+  abstract. \\[1em]
 
-\section{First section}
-\subsection{Subsection}
-\subsubsection{Subsubsection}
+  {\bf Keywords}: Keyword1 --  Keyword2 -- Keyword3 -- Keyword4 --
+  Keyword5 
+}
 
-TARATATA
+\maketitle
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+The introduction ..
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Section 2}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed non risus.
 Suspendisse lectus tortor, dignissim sit amet, adipiscing nec, ultricies
-
 sed, dolor. Cras elementum ultrices diam. Maecenas ligula massa, varius
@@
 pellentesque fermentum. Maecenas adipiscing ante non diam sodales
-hendrerit. Ut velit mauris, egestas sed, gravida nec, ornare ut, mi.
-Aenean ut orci vel massa suscipit pulvinar. Nulla sollicitudin. Fusce
-varius.
+hendrerit.
 
-\begin{equation}
-  \label{eq:001}
-  E = mc^2
-\end{equation}
+Ut velit mauris, egestas sed, gravida nec, ornare ut, mi. Aenean ut orci
+vel massa suscipit pulvinar. Nulla sollicitudin. Fusce varius, ligula
+non tempus aliquam, nunc turpis ullamcorper nibh, in tempus sapien eros
+vitae ligula. Pellentesque rhoncus nunc et augue. Integer id felis.
+Curabitur aliquet pellentesque diam. Integer quis metus vitae elit
+lobortis egestas. Lorem ipsum dolor sit amet, consectetuer adipiscing
+elit. Morbi vel erat non mauris convallis vehicula. Nulla et sapien.
+Integer tortor tellus, aliquam faucibus, convallis id, congue eu, quam.
+Mauris ullamcorper felis vitae erat. Proin feugiat, augue non elementum
+posuere, metus purus iaculis lectus, et tristique ligula justo vitae
+magna.
 
-Ligula non tempus aliquam, nunc turpis ullamcorper nibh, in
-tempus sapien eros vitae ligula. Pellentesque rhoncus nunc et augue.
-Integer id felis. Curabitur aliquet pellentesque diam. Integer quis
-metus vitae elit lobortis egestas. Lorem ipsum dolor sit amet,
-consectetuer adipiscing elit. Morbi vel erat non mauris convallis
-vehicula. Nulla et sapien. Integer tortor tellus, aliquam faucibus,
-convallis id, congue eu, quam. Mauris ullamcorper felis vitae erat.
-Proin feugiat, augue non elementum posuere, metus purus iaculis lectus,
-et tristique ligula justo vitae magna. Aliquam convallis sollicitudin
-purus. Praesent aliquam, enim at fermentum mollis, ligula massa
-adipiscing nisl, ac euismod nibh nisl eu lectus. Fusce vulputate sem at
-sapien. Vivamus leo. Aliquam euismod libero eu enim. Nulla nec felis sed
-leo placerat imperdiet. Aenean suscipit nulla in justo. Suspendisse
-cursus rutrum augue. Nulla tincidunt tincidunt mi. Curabitur iaculis,
-lorem vel rhoncus faucibus, felis magna fermentum augue, et ultricies
-lacus lorem varius purus. Curabitur eu amet.
+Aliquam convallis sollicitudin purus. Praesent aliquam, enim at
+fermentum mollis, ligula massa adipiscing nisl, ac euismod nibh nisl eu
+lectus. Fusce vulputate sem at sapien. Vivamus leo. Aliquam euismod
+libero eu enim. Nulla nec felis sed leo placerat imperdiet. Aenean
+suscipit nulla in justo. Suspendisse cursus rutrum augue. Nulla
+tincidunt tincidunt mi. Curabitur iaculis, lorem vel rhoncus faucibus,
+felis magna fermentum augue, et ultricies lacus lorem varius purus.
+Curabitur eu amet.
 
-%%%
-\subsection{Table}
-This is a sample table referred to as Table~\ref{tab:001}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Section 3}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed non risus.
+Suspendisse lectus tortor, dignissim sit amet, adipiscing nec, ultricies
+sed, dolor. Cras elementum ultrices diam. Maecenas ligula massa, varius
+a, semper congue, euismod non, mi. Proin porttitor, orci nec nonummy
+molestie, enim est eleifend mi, non fermentum diam nisl sit amet erat.
+Duis semper. Duis arcu massa, scelerisque vitae, consequat in, pretium
+a, enim. Pellentesque congue. Ut in risus volutpat libero pharetra
+tempor. Cras vestibulum bibendum augue. Praesent egestas leo in pede.
+Praesent blandit odio eu enim. Pellentesque sed dui ut augue blandit
+sodales. Vestibulum ante ipsum primis in faucibus orci luctus et
+ultrices posuere cubilia Curae; Aliquam nibh. Mauris ac mauris sed pede
+pellentesque fermentum. Maecenas adipiscing ante non diam sodales
+hendrerit.
 
-\begin{table}[!ht]
-  \begin{center}      \caption{Exemple de table} \label{tab:001}
-    \begin{tabularx}{\textwidth}
-      {>{\lratio{0.9}}Y>{\lratio{0.9}}Y>{\lratio{0.9}}Y>{\lratio{1.3}}Y}
-      \hline \rowcolor[gray]{0.98} {Parameter} & {Distribution} & {Mean} &
-      {Coefficient of variation} \\ \hline
-      {$L$}		& {Lognormal}		& {$1$ m}		& {$3\%$}		\\
-      {$b$}		& {Lognormal}		& {$10$ cm}		& {$3\%$}		\\
-      {$h$}		& {Lognormal}		& {$1$ cm}		& {$3\%$}		\\
-      {$F$}		& {Lognormal}		& {$200$ N}		& {$20\%$}		\\
-      {$E_f$}		& {Lognormal}		& {$300$ GPa}		& {$15\%$}		\\
-      {$E_m$}		& {Lognormal}		& {$10$ GPa}		& {$15\%$}		\\
-      {$\rho_f$}	& {Lognormal}		& {$1800$ kgm$^{-3}$}	& {$3\%$}		\\
-      {$\rho_m$}	& {Lognormal}		& {$1200$ kgm$^{-3}$}	& {$3\%$}		\\
-      {$f$} & {Lognormal} & {$0.5$} & {$10\%$} \\ \hline
-    \end{tabularx}
-  \end{center}
-\end{table}
+Ut velit mauris, egestas sed, gravida nec, ornare ut, mi. Aenean ut orci
+vel massa suscipit pulvinar. Nulla sollicitudin. Fusce varius, ligula
+non tempus aliquam, nunc turpis ullamcorper nibh, in tempus sapien eros
+vitae ligula. Pellentesque rhoncus nunc et augue. Integer id felis.
+Curabitur aliquet pellentesque diam. Integer quis metus vitae elit
+lobortis egestas. Lorem ipsum dolor sit amet, consectetuer adipiscing
+elit. Morbi vel erat non mauris convallis vehicula. Nulla et sapien.
+Integer tortor tellus, aliquam faucibus, convallis id, congue eu, quam.
+Mauris ullamcorper felis vitae erat. Proin feugiat, augue non elementum
+posuere, metus purus iaculis lectus, et tristique ligula justo vitae
+magna.
 
-%%% 
-\subsection{Figure}
-This is a sample figure referred to as Figure~\ref{fig:001}.
+Aliquam convallis sollicitudin purus. Praesent aliquam, enim at
+fermentum mollis, ligula massa adipiscing nisl, ac euismod nibh nisl eu
+lectus. Fusce vulputate sem at sapien. Vivamus leo. Aliquam euismod
+libero eu enim. Nulla nec felis sed leo placerat imperdiet. Aenean
+suscipit nulla in justo. Suspendisse cursus rutrum augue. Nulla
+tincidunt tincidunt mi. Curabitur iaculis, lorem vel rhoncus faucibus,
+felis magna fermentum augue, et ultricies lacus lorem varius purus.
+Curabitur eu amet.
 
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=3cm]{Dummy}
-  \caption{Title} \label{fig:001}
-\end{figure}
+Ut velit mauris, egestas sed, gravida nec, ornare ut, mi. Aenean ut orci
+vel massa suscipit pulvinar. Nulla sollicitudin. Fusce varius, ligula
+non tempus aliquam, nunc turpis ullamcorper nibh, in tempus sapien eros
+vitae ligula. Pellentesque rhoncus nunc et augue. Integer id felis.
+Curabitur aliquet pellentesque diam. Integer quis metus vitae elit
+lobortis egestas. Lorem ipsum dolor sit amet, consectetuer adipiscing
+elit. Morbi vel erat non mauris convallis vehicula. Nulla et sapien.
+Integer tortor tellus, aliquam faucibus, convallis id, congue eu, quam.
+Mauris ullamcorper felis vitae erat. Proin feugiat, augue non elementum
+posuere, metus purus iaculis lectus, et tristique ligula justo vitae
+magna.
 
-%%% 
-\subsection{Notation}
-A set of standard notation is defined in the file
-\texttt{bstnotations.sty} and shall be used whenever justified.
+Aliquam convallis sollicitudin purus. Praesent aliquam, enim at
+fermentum mollis, ligula massa adipiscing nisl, ac euismod nibh nisl eu
+lectus. Fusce vulputate sem at sapien. Vivamus leo. Aliquam euismod
+libero eu enim. Nulla nec felis sed leo placerat imperdiet. Aenean
+suscipit nulla in justo. Suspendisse cursus rutrum augue. Nulla
+tincidunt tincidunt mi. Curabitur iaculis, lorem vel rhoncus faucibus,
+felis magna fermentum augue, et ultricies lacus lorem varius purus.
+Curabitur eu amet.
 
-%%%
-\subsection{References}
-Citations are managed with \textsc{Bib}\TeX. A data base (\eg
-\texttt{biblioUQ.bib}) is used to gather all the bibliography. All
-papers of interest for the PhD shall be stored in this
-\texttt{bib}-file. JabRef is a good Java-based reference manager that
-works under all operating systems and allows a simple management of the references.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% References
+\nocite{SudretHDR}
 
-In order to use it, the commands \texttt{$\backslash$citep} and
-\texttt{$\backslash$citet} from the \texttt{natbib} package are used:
-\begin{itemize}
-\item If the citation appears {\em within} a sentence, it is referred to
-  using \texttt{$\backslash$citet}, as in: 
-  \begin{quotation}
-    \citet{Bourinet2011} introduced support vector machines and subset
-    simulation in order to compute small probabilities of failure.
-  \end{quotation}
-\item If the citation appears {\em at the end} of the sentence, \ie
-  using parenthesis, the \texttt{$\backslash$citep} command shall be
-  used, as in:
-  \begin{quotation}
-    The use of support vector machines for structural reliability
-    analysis was proposed recently
-    \citep{Basudhar2008a,Basudhar2008b,Bourinet2011}.
-  \end{quotation}
-\end{itemize}
-
-% References
-\renewcommand{\bibname}{References}
 \bibliographystyle{chicago}
-\bibliography{biblioUQ}
-
-\label{end}
+\bibliography{biblioRSUQ}
 \end{document}

### 2019-05-07 styles/texmf/tex/latex/rsuqreport/rsuqreport_template.tex
Update presentation

--- 2019-05-07 styles/texmf/tex/latex/MascotNum/MascotNumTemplate.tex
@@
-% % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% Template file for MascotNum 2014 Phd Student papers 
-% November 4th, 2013
-% (c) Stefano Marelli, Bruno Sudret
-% Chair of Risk, Safety, and Uncertainty Quantification 
-% ETH Zürich
-% 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\documentclass{MascotNumAbstract}
+% Template using the rsuqreport class for producing standard reports from the Chair of Risk, Safety 
+% and Uncertainty Quantification in ETH Zurich.
+% Copyright 2013, Stefano Marelli and Bruno Sudret, all rights reserved. 
+% Please contact Stefano Marelli (marelli@ibk.baug.ethz.ch) for any template-related enquiries.
+\documentclass{rsuqreport}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % Beginning of the personal information section % % %
-% % % PLEASE NOTE: All of the fields are mandatory! % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% additional packages/package options may be added here
 
-% Authors names, in the form 'initials surname', as in:
-% J. Smith
- \author{A. PhDStudent}
-% Short form of the author names (will appear in the odd/even pages of the abstracts)
- \shortauthor{PhDStudent} 
-% Corresponding author
- \correspondingauthor{A. PhDStudent}
-% Corresponding author address
- \firstauthoraddress{\emph{Chair of Risk, Safety and Uncertainty Quantification}, ETH Z\"urich, Wolfgang-Pauli-strasse 15, CH-8093 Z\"urich, Switzerland}
-% University where the MSc was acquired
- \masteruniversity{University where the master's degree was completed}
-% Current university (PhD)
- \phduniversity{University where the Ph.D is prepared}
-% Expected phd duration. Format:
- \phdtime{2012-2015}
-% Supervisors and affiliations  
- \supervisors{Prof. Supervisor1 (University1) and Prof. Supervisor2
-   (University2) and Dr. Supervisor3 (Company)}
-% Webpage of the author or of the university group
- \webaddress{http://www.ibk.ethz.ch/su/index_EN}
-% Contact mail
- \contactmail{marelli@ibk.baug.ethz.ch}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% THE FOLLOWING INFORMATION NEEDS TO BE PROVIDED TO PROPERLY COMPILE THE REPORT INTESTATION. 	  %
+% PLEASE NOTE THAT THE FIELDS CAN BE LEFT EMPTY, BUT THEY MUST NOT BE REMOVED!					  %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-% Title of the abstract
- \title{MascotNum2014 conference - Template abstract for the PhD papers} 
-% short version of the title for the running headers
- \shorttitle{Short title for the abstract}
+% Report title. Due to restriction on the template design, please make sure it is at most 3 lines 
+% long
+\title{RSUQ Report Template}
+% List of authors (comma separated) as it will appear on the paper
+\author{Ann Author, Another Author}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % %   End of the personal information section 	% % %
-% PLEASE NOTE: All of the fields are mandatory!     % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% Name of the client the report is addressed to
+\clientname{Enterprise Inc.}
+% Identifier for the contract
+\contractref{Research Agreement n$^\circ$ AB12345}
+% Contact person for the client
+\contactname{Dr. G. Freeman}
+% Address of the client (Can be multi-line text)
+\clientaddress{	Stefano-Franscini-Platz 5\\ 
+				CH-8093 Z\"urich\\
+				Switzerland }
+% ETH Project number related to the report
+\ethprojectnum{312345}
+% Reference name for the report
+\reportref{R-312345-001/A/}
 
-% full abstract text
-  \begin{document}
-
+% Abstract of the report. May contain any type of formatting
+\reportabstract{
 	Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus
@@
 
+}
+\keywords{Lorem, ipsum}
+
+% BEGINNING OF THE REAL DOCUMENT CONTENTS
+
+\begin{document}
+
+\section{First Section}
+\subsection{Subsection}
+\subsubsection{Subsubsection}
+TARATATATA
+
 Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat
@@
 
+\begin{equation}
+E = mc^2
+\label{eqn: Einstein}
+\end{equation}
+
 Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae
@@
 
-  Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a
-  faucibus semper, leo velit ultricies tellus, ac venenatis arcu wisi
-  vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis
-  posuere, turpis lacus congue quam, in hendrerit risus eros eget felis.
-  Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor.
-  Nulla facilisi. Sed a turpis eu lacus commodo facilisis. Morbi
-  fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-  vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis
-  cursus enim ut augue. Cras ac magna. Cras nulla. Nulla egestas.
-  Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel
-  est.  Curabitur consectetuer.
+\subsection{Table}
+This is a sample table referred to as Table \ref{table: random variables}
+\begin{table}[h]
+	\centering
 
-  Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit
-  amet, laoreet vitae, arcu. Aenean faucibus pede eu ante. Praesent enim
-  elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros,
-  malesuada sit amet, fermentum eu, sodales cursus, magna. Donec eu
-  purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas
-  dui, et convallis elit erat sed nulla. Donec luctus. Curabitur et
-  nunc.  Aliquam dolor odio, commodo pretium, ultricies non, pharetra
-  in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas
-  vel, odio.
+	\begin{tabular}{cccc}
+		\hline
+		Parameter & Distribution & Mean & Coefficient of variation \\ \hline
+		    L     &  Lognormal   &  1m  &           3\%            \\
+		    b     &  Lognormal   & 10cm &           3\%            \\
+		    h     &  Lognormal   & 1cm  &           3\%            \\ \hline
+	\end{tabular}
+	\caption{Example of a table}
+	\label{table: random variables}
 
-  Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio.
-  Sed vehicula hendrerit sem. Duis non odio. Morbi ut dui. Sed accumsan
-  risus eget odio. In hac habitasse platea dictumst. Pellentesque non
-  elit. Fusce sed justo eu urna porta tincidunt. Mauris felis odio,
-  sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
-  pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis
-  congue purus metus ultricies tellus. Proin et quam. Class aptent
-  taciti sociosqu ad litora torquent per conubia nostra, per inceptos
-  hymenaeos. Praesent sapien turpis, fermentum vel, eleifend faucibus,
-  vehicula eu, lacus.
+\end{table}
 
-% Short biography
-  \vfill
+\section{Figures}
+This is a sample figure referred to as Figure \ref{img: test figure}.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width = .3\textwidth]{ReportBackGround_75dpi_1MP.jpg}
+	\caption{This is a sample figure}
+	\label{img: test figure}
+\end{figure}
 
-  {\bf Short biography --}~~ Each PhD student is asked to present in
-  max. 5 lines his/her background and the context of the PhD thesis, the
-  sources of funding, links with industry, etc.
+\section{Notation}
+A set of standard notation is defined in the file \verb|bstnotation.sty| and shall be 
+used 
+whenever justified.
 
-\vspace*{1cm}
+\section{References}
+Citations are managed with \textsc{Bib}\TeX. A data base (\eg{} \verb|test.bib|) iis 
+used to gather 
+all the bibliography. All papers of interest shall be stored in this \verb|bib| file.
+
+In order to use it, the commands \verb|\citep| and \verb|\citet| from the 
+\verb|natbib| package are 
+used:
+\begin{itemize}
+\item If the citation appears \emph{within} a sentence, it is referred to using 
+\verb|\citet|, as 
+in:  
+	\begin{itemize}
+		\item[] \citet{Bourinet2011} introduced support vector machines and subset 
+		simulation in 
+		order to compute small probabilities of failure
+	\end{itemize}
+\item If the citation appears \emph{at the end} of the sentence, \ie{} using 
+parenthesis, the 
+\verb|\citep| command shall be used, as in:\\
+\begin{itemize}
+	\item[] The use of support vector machines for structural reliability analysis was 
+	proposed 
+		recently \citep{Bourinet2011,Basudhar2008a,Basudhar2008b}.
+\end{itemize}
+\end{itemize}
+
+\bibliographystyle{chicago}
+\bibliography{testbib}
 

### 2019-05-07 latex/BeamerGPR.tex
Update presentation slides

@@
 
-\title[Notes on GPR]{Notes on Gaussian Process Regression (GPR)}
+\title[UQWorld]{UQWorld: an Applied UQ Community}
 
@@
 
-\date[28.03.2019]
+\date[09.05.2019]
 
@@
 \usepackage{pifont}
+\usepackage{booktabs}% http://ctan.org/pkg/booktabs
+\newcommand{\tabitem}{~~\llap{\textbullet}~~}
 %\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
@@
 %===============================================================================
-\begin{frame}{UQLab users}
+\begin{frame}{Background}
 
-Ideas for our UQ community are initiated
-from our understanding of the \emph{natural} audience, \textbf{UQLab users}:
+We tried to get some ideas for our UQ community based on
+our understanding of the \emph{natural} audience, i.e., \textbf{UQLab users}:
 
@@
   we don't know much about them or how they are using UQLab\footnote{Which are not the point of registration.
-For the actual reasons on why registration is required, see Stefano's blog on \emph{Why do we ask you to register to get UQLab?
-Why does the "core" folder contain obscured files?}}.
+  For the actual reasons on why registration is required,
+  see Stefano's blog on \emph{Why do we ask you to register to get UQLab? Why does the "core" folder contain obscured files?}
+  in \texttt{UQWorld}}.
 \end{itemize}
@@
 
-  Many are about registration, license, and installations:
+Many are about registration, installations, and license:
+
 \begin{itemize}
+  \item From:$\blacksquare@\blacksquare$.com, Subject: Registration, captcha
+    \begin{quotation}
+      Trying to register for downloading UQLab, I always fail to find the captcha.
+      Could you please check it? I'd be surprised to find out that I am a bot :)
+    \end{quotation}
+
+  \item From:$\blacksquare.\blacksquare@\blacksquare$.edu, Subject: problem while installing uqlab
+    \begin{quotation}
+      i have problems installing on MATLAB 2010b, the version 2014a seems to work ok. i just want to let you know about that. 
+    \end{quotation}
+
   \item From:$\blacksquare@\blacksquare$.fr, Subject: Loose the licence file
@@
     \end{quotation}
-  \item From:$\blacksquare@\blacksquare$.com, Subject: Registration, captcha
-  \begin{quotation}
-  Trying to register for downloading UQLab, I always fail to find the captcha. Could you please check it? I'd be surprised to find out that I am a bot :)
-\end{quotation}
-\item From:$\blacksquare.\blacksquare@\blacksquare$.edu, Subject: problem while installing uqlab
-\begin{quotation}
-  i have problems installing on MATLAB 2010b, the version 2014a seems to work ok. i just want to let you know about that. 
-\end{quotation}
+
 \end{itemize}
+
 \end{frame}
@@
 \begin{itemize}
-  \item From: david.$\blacksquare@\blacksquare$.de, Subject: Citing UQLab
+  \item From: $\blacksquare@\blacksquare$.de, Subject: Citing UQLab
   \begin{quotation}
     As I won't have the chance to employ it in my work, \textbf{I would like to include it in my literature section to raise awareness for students after me}.
-Unfortunately, I couldn't find how to cite UQLab.
-Any recommendations?
+    Unfortunately, I couldn't find how to cite UQLab. Any recommendations?
   \end{quotation}
@@
   \begin{quotation}
-    I haven't started to use UQlab yet but at a glance let me tell you that it seems a very nice job!
+    I haven't started to use UQlab yet but at a glance \textbf{let me tell you that it seems a very nice job!}
   \end{quotation}
@@
 \begin{itemize}
-  \item From:$\blacksquare@\blacksquare$.com, Subject: CV as a parameter estimation method
-  \begin{quotation}
-    Hey, 
-    I would like to ask where I can find more explanation about how cross validation is used in estimating parameters of kriging models. The manuel didn't help much. 
-  \end{quotation}
   \item From:$\blacksquare@\blacksquare$.edu, Subject: Unregister
@@
     Thank you!
+  \end{quotation}
+\end{itemize}
+
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}{UQLab users: A glimpse from support emails}
+
+Some are (downright) hard to read,
+\begin{itemize}
+  \item From: $\blacksquare@\blacksquare$.edu.cn, Subject: Matlab code by Dr. Moustapha w.r.t. the fascinating Quantile-based RBDO
+  \begin{quotation}
+    Good dinner Dr. Moustapha \\
+    Your catchy Quantile-based RBDO bring up new ideas for our RBDO world.
+    If Dr. Moustapha is going to need allies or assistants for your idea to gain momentum, sincere hope for good cooperation (fans) between us (of yours) \texttt{\textasciitilde.\textasciitilde}!
+    Actually, me is a current Master student w.r.t. Reliabil \& Syst Engn.
+    If I make the decision to embark on a PhD, your QB-RBDO is really fascinating for me.(Wow! Such a productve and effective methodology for practical applications.That's terrific!)
   \end{quotation}
@@
 
+Many user online communities started as support communities, but if \emph{only} for that:
+\begin{itemize}
+  \item it'll be too restrictive % If UQ is somehow already a niche, then UQLab users would even be smaller bunch of audience
+  \item it's not very aspiring
+\end{itemize}
+\\~\\
+Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.
+\\~\\
+Besides, there seems to be an opportunity...
+\\~\\
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}[t]{Other UQ Online Communities}
+
+\begin{columns}
+  \column{0.5\textwidth}
+  \begin{figure}
+    \includegraphics[width=0.70\textwidth]{../figures/dakota}
+  \end{figure}
+
+  \column{0.5\textwidth}
+  \begin{figure}
+    \includegraphics[width=0.45\textwidth]{../figures/openTurns}
+  \end{figure}
+\end{columns}
+
+\begin{itemize}
+  \item Dakota maintains mailing lists,
+        but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for a community}.
+  \item OpenTurns maintains a blog, but not maintained.
+  \item Otherwise, zero relevant results from Google search
+        for ``uncertainty quantification community'' or ``uncertainty quantification forum''.
+\end{itemize}
+
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}[t]{Ideas for an Online Community}
+
+\begin{tabularx}{\textwidth}{XX}
+  \hline
+  Questions                            & Answers \\
+  \hline
+  \emph{What will the community be about?}               & About UQ and UQLab-related topics \\
+  \emph{Who is the community for?}                       & UQ practitioners, researchers, and UQLab users \\
+
+  \emph{What is the purpose or goal of the community? What UQLab community strive for?}
+  & \tabitem Be a place to discuss about, share, learn, and get help in topics related to UQ, from beginners to advanced \\
+  & \tabitem Be the definitive community-powered home for UQLab support and best practices \\
+
+  \emph{What will happen in the community?}          & Selection of various contents (editorial and user-generated), free form discussion, knowledge base \\
+
+  \hline
+\end{tabularx}
+
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}[t]{Ideas for an Online Community}
+
 \end{frame}
@@
 \section{Tools for an Online Community}
+
+\begin{frame}[t]{Tools for an Online Community}
+
+  \begin{columns}
+    \column{0.50\textwidth}
+    \begin{minipage}[c][0.80\textheight][c]{\linewidth}
+      \begin{figure}
+        \centering
+        \includegraphics[width=1.0\linewidth]{../figures/communityPlatform}
+      \end{figure}
+    \end{minipage}
+
+    \column{0.50\textwidth}
+  \begin{itemize}
+    \item Between 2016--2019, about 83 papers are published in which UQLab is used as an analysis tool.
+    \item already live at \texttt{uqworld.org}
+  \end{itemize}
+  \hfill
+ \end{columns}
+
+\end{frame}
 
@@
 
-The largest chunk of space in \texttt{UQWorld} caters to UQ practitioners---from the uninitiated to skilled---regardless the software tool they are using:
+The largest chunk of space in \texttt{UQWorld} caters to UQ practitioners---from the uninitiated to experts---regardless the software tool they are using:
 

### 2019-05-07 latex/BeamerGPR.tex
Update slide on the goal of our community

@@
 %===============================================================================
-\begin{frame}[t]{Ideas for an Online Community}
+\begin{frame}[t]{A (long) sentence for a UQ online community}
 
-\begin{tabularx}{\textwidth}{XX}
-  \hline
-  Questions                            & Answers \\
-  \hline
-  \emph{What will the community be about?}               & About UQ and UQLab-related topics \\
-  \emph{Who is the community for?}                       & UQ practitioners, researchers, and UQLab users \\
+We aim our UQ online community to be a community of:
 
-  \emph{What is the purpose or goal of the community? What UQLab community strive for?}
-  & \tabitem Be a place to discuss about, share, learn, and get help in topics related to UQ, from beginners to advanced \\
-  & \tabitem Be the definitive community-powered home for UQLab support and best practices \\
+\begin{itemize}
+  \item UQ practitioners and researchers and
+  \item UQLab users
+\end{itemize}
 
-  \emph{What will happen in the community?}          & Selection of various contents (editorial and user-generated), free form discussion, knowledge base \\
+across different level of expertise, from beginners to advanced, to:
 
-  \hline
-\end{tabularx}
+\begin{itemize}
+  \item learn the basics as well as new things in UQ;
+  \item discuss UQ-related topics, share news, knowledge and experience, and showcase expertise;
+  \item get and give help in using UQLab and discuss UQLab features and its continuous development.
+\end{itemize}
 
-\end{frame}
-%===============================================================================
+%\begin{tabularx}{\textwidth}{XX}
+%  \hline
+%  Questions                            & Answers \\
+%  \hline
+%  \emph{What will the community be about?}               & About UQ and UQLab-related topics \\
+%  \emph{Who is the community for?}                       & UQ practitioners, researchers, and UQLab users \\
 
-%===============================================================================
-\begin{frame}[t]{Ideas for an Online Community}
+%  \emph{What is the purpose or goal of the community? What UQLab community strive for?}
+%  & \tabitem Be a place to discuss about, share, learn, and get help in topics related to UQ, from beginners to advanced \\
+%  & \tabitem Be the definitive community-powered home for UQLab support and best practices \\
+
+%  \emph{What will happen in the community?}          & Selection of various contents (editorial and user-generated), free form discussion, knowledge base \\
+
+%  \hline
+%\end{tabularx}
 
@@
 
+%===============================================================================
 \begin{frame}[t]{Tools for an Online Community}

### 2019-05-07 latex/BeamerGPR.tex
Minor edit

@@
 We tried to get some ideas for our UQ community based on
-our understanding of the \emph{natural} audience, i.e., \textbf{UQLab users}:
+our understanding of the \emph{apparent} audience, i.e., \textbf{UQLab users}:
 
@@
 
-How can we know more of our audience up to the present?
+How can we know more of our audience, up to the present?
 
@@
         but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for a community}.
-  \item OpenTurns maintains a blog, but not maintained.
+  \item OpenTurns (barely) maintains a blog (last post july 2019, peak posts in 2011, no public discussions) 
   \item Otherwise, zero relevant results from Google search
@@
 \begin{itemize}
-  \item UQ practitioners and researchers and
+  \item UQ practitioners and researchers, and
   \item UQLab users

### 2019-05-08 latex/uqworld-presentation.tex
Rename file

--- 2019-05-07 latex/BeamerGPR.tex
@@
   For the actual reasons on why registration is required,
-  see Stefano's blog on \emph{Why do we ask you to register to get UQLab? Why does the "core" folder contain obscured files?}
+  see Stefano's blog on \emph{Why a licensing system? Is UQLab really open source?}
   in \texttt{UQWorld}}.
@@
 
+% Ideas mean who is for, what is it about
 \end{frame}
@@
   \begin{quotation}
-    I haven't started to use UQlab yet but at a glance \textbf{let me tell you that it seems a very nice job!}
+    \textbf{I haven't started to use UQlab yet} but at a glance \textbf{let me tell you that it seems a very nice job!}
   \end{quotation}
@@
 
-Some are (downright) hard to read,
+Some are a bit hard to read,
 \begin{itemize}
@@
     \bibitem[Xie and Schenkendorf, 2019]{Xie2019}
-    Xiangzhong Xie and Ren\'e Schenkendorf
-    \newblock Stochastic back-off-based robust process design for continuous crystallization of ibuprofen, {\em Computers and Chemical Engineering}, vol. 124, 2019.
+    Xiangzhong Xie and Ren\'e Schenkendorf,
+    \newblock Stochastic back-off-based robust process design for continuous crystallization of ibuprofen, {\em Computers and Chemical Engineering}, 2019.
 
@@
     Xiangzhong Xie, R\"udiger Ohs, A. C. Spiess, Ulrike Krewer, and Ren\'e Schenkendorf,
-    \newblock Moment-independent sensitivity analysis of enzyme-catalyzed reactions with correlated model parameters, {\em IFAC-PapersOnLine}, vol. 51, 2018.
+    \newblock Moment-independent sensitivity analysis of enzyme-catalyzed reactions with correlated model parameters, {\em IFAC-PapersOnLine}, 2018.
 
@@
     \bibitem[Schenkendorf et al., 2017]{Schenkendorf2017}
-    Ren\'e Schenkendorf, Xiangzhong Xie, and Ulrike Krewer
+    Ren\'e Schenkendorf, Xiangzhong Xie, and Ulrike Krewer,
     \newblock An efficient polynomial chaos expansion strategy for active fault identification of chemical processes, {\em Computer Aided Chemical Engineering}, 2017.
@@
 
+% Users need help, they might demand something, and some are ready to give back.
+% Audience from users is readily available (_you build it, and they will come_).
 Many user online communities started as support communities, but if \emph{only} for that:
 \begin{itemize}
-  \item it'll be too restrictive % If UQ is somehow already a niche, then UQLab users would even be smaller bunch of audience
+  \item it'll be too restrictive % If UQ is somehow already a niche, then UQLab users would even be smaller bunch of audience.
+We attached too much the growth of the community with the growth of UQLab.
+Finally, there are times that you yourself would be more interested talking about UQ than just UQLab.
   \item it's not very aspiring
 \end{itemize}
-\\~\\
+%\\~\\
 Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.
-\\~\\
+%\\~\\
 Besides, there seems to be an opportunity...
-\\~\\
+
+% Makes sense because it also fits with the Chair's mission:
+% It promotes an active collaboration with research groups in ETH and in other universities in order to disseminate the good practices and associated tools for uncertainty quantification.
+UQLab is not a pre-requisite.
 \end{frame}
@@
 %===============================================================================
-\begin{frame}[t]{Other UQ Online Communities}
+\begin{frame}[t]{Other UQ Online Communities?}
 
@@
   \item Dakota maintains mailing lists,
-        but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for a community}.
-  \item OpenTurns (barely) maintains a blog (last post july 2019, peak posts in 2011, no public discussions) 
+        but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for (starting) a community.}.
+  \item OpenTurns maintains a blog, or not (last post July 2018, peak posts 2011, no public discussions). 
   \item Otherwise, zero relevant results from Google search
@@
 
-across different level of expertise, from beginners to advanced, to:
+across different level of expertise---from the unitiated to experts---to:
 
@@
 \end{itemize}
+
+%such that it becomes:
+%\begin{itemize}
+%  \item the definitive place to discuss and share online topics related to UQ;
+%  \item the home for UQLab users (incl., at some point, external contributors) online community.
+%\end{itemize}
 
@@
     \column{0.50\textwidth}
+    Three possible platforms or tools were considered:
   \begin{itemize}
-    \item Between 2016--2019, about 83 papers are published in which UQLab is used as an analysis tool.
-    \item already live at \texttt{uqworld.org}
+    \item Wix: What we already have (\texttt{uqlab.com}) plus a forum plugin.
+    \item Wordpress: Entirely new website (\textbf{a blog, with a forum} plugin).
+    \item Discourse: Entirely new website (\textbf{a forum, with some kind of blog}).
   \end{itemize}
+  We decided to go on with Discourse.
+% Because of relative simplicity, more out-of-the-box modern forum, lower bar of participation, great search functionalities.
+In Wordpress, so much thinkering in the forum plugin to have it on par with more modern forum.
+It's about the amount of tinkering we want.
   \hfill
+
  \end{columns}
-
+% mainly forum plus some (limited) customization for blogs
 \end{frame}
 
-\section{UQWorld}
+\section{UQWorld (with Demo)}
 
@@
   \begin{columns}
-    \column{0.35\textwidth}
+    \column{0.30\textwidth}
     \begin{minipage}[c][0.85\textheight][c]{\linewidth}
@@
 
-    \column{0.65\textwidth}
+    \column{0.70\textwidth}
     \begin{itemize}
-      \item Between 2016--2019, about 83 papers are published in which UQLab is used as an analysis tool.
-      \item already live at \texttt{uqworld.org}
+      \item An online community platform for applied UQ.
+      \item Already live (but not public) at \texttt{uqworld.org}.
+      \item Will be open to all: exploration (browsing) is public,
+            but any participation requires registration.
+      \item Three main categories: 
+      \begin{itemize}
+        \item Learn and discuss UQ topics (\emph{All About UQ})
+        \item News, updates, case studies, other community resources, and meta-discussion (\emph{UQ Resources})
+        \item UQLab support \& Development (\emph{UQ with UQLab})
+      \end{itemize}
     \end{itemize}
     \hfill
-  \end{columns}
-
-\end{frame}
-%===============================================================================
-
-%===============================================================================
-\begin{frame}[t]{UQWorld: Structure and organization}
-
-\texttt{UQWorld} is organized into three main categories:
     \begin{columns}
@@
     \end{columns}
-
-\begin{itemize}
-  \item \emph{All About UQ} contains the free UQ discussion forum and the Chair's published post (\textbf{UQ-centered} space).
-  \item \emph{UQ Resources} contains news, updates, case studies, and other resources from UQ community at large (\textbf{UQ-centered} space).
-  \item \emph{UQ with UQLab} is the corner for UQLab users, a place to get help with UQLab, as well as updates from the Developer Team (\textbf{UQLab-centered} space).
-\end{itemize}
+  \end{columns}
 
@@
 %===============================================================================
-\begin{frame}[t]{UQWorld: An Applied UQ Community}
+%\begin{frame}[t]{UQWorld: Structure and organization}
 
-The largest chunk of space in \texttt{UQWorld} caters to UQ practitioners---from the uninitiated to experts---regardless the software tool they are using:
+%\texttt{UQWorld} is organized into three main categories:
+%\begin{columns}
+ % \column{0.3\textwidth}
+  %\begin{figure}
+   % \includegraphics[width=0.70\textwidth]{../figures/all-about-uq_512}
+   % \caption*{All About UQ}
+  %\end{figure}
 
-\begin{itemize}
-  \item \emph{UQ Discussion Forum}: A lightly-moderated forum to ask, discuss, and share (Examples: Introduce projects and UQ methods applied, )
-  \item \emph{Chair's Blog} (Example: Bruno's posts on \emph{Getting started with UQ} and \emph{How to define my probabilistic input distributions?}).
-  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
-  \item \emph{Case studies} (Example: Paul's post on the calibration of heat transfer model).
-  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
-\end{itemize}
+ % \column{0.3\textwidth}
+ % \begin{figure}
+ %   \includegraphics[width=0.65\textwidth]{../figures/uq-resources_512}
+ %   \caption*{UQ Resources}
+ % \end{figure}
 
-\end{frame}
+ % \column{0.3\textwidth}
+ % \begin{figure}
+ %   \includegraphics[width=0.6\textwidth]{../figures/uq_with_uqlab_512}
+ %   \caption*{UQ with UQLab}
+ % \end{figure}
+%\end{columns}
+
+%\begin{itemize}
+  %\item \emph{All About UQ} contains the free UQ discussion forum and the Chair's published post (\textbf{UQ-centered} space).
+  %\item \emph{UQ Resources} contains news, updates, case studies, and other resources from UQ community at large (\textbf{UQ-centered} space).
+  %\item \emph{UQ with UQLab} is the corner for UQLab users, a place to get help with UQLab, as well as updates from the Developer Team (\textbf{UQLab-centered} space).
+%\end{itemize}
+
+%\end{frame}
 %===============================================================================
@@
 %===============================================================================
-\begin{frame}[t]{UQWorld: The UQLab User Community}
+%\begin{frame}[t]{UQWorld: An Applied UQ Community}
 
-\texttt{UQWorld} is the definitive UQLab user community:
+%The largest chunk of space in \texttt{UQWorld} caters to UQ practitioners---from the uninitiated to experts---regardless the software tool they are using:
 
-\end{frame}
+%\begin{itemize}
+%  \item \emph{UQ Discussion Forum}: A lightly-moderated forum to ask, discuss, and share (Examples: Introduce projects and UQ methods applied, )
+%  \item \emph{Chair's Blog} (Example: Bruno's posts on \emph{Getting started with UQ} and \emph{How to define my probabilistic input distributions?}).
+%  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
+%  \item \emph{Case studies} (Example: Paul's post on the calibration of heat transfer model).
+%  \item \emph{News and Announcements} (Example: Paul's post on the calibration of heat transfer model).
+%\end{itemize}
+
+%\end{frame}
 %===============================================================================
@@
 %===============================================================================
-\begin{frame}[t]{UQWorld: Structure and organization}
+\begin{frame}[t]{UQWorld: Access and organization}
 
-Member write access to categories within \texttt{UQWorld} is controlled;
+Members' write access to certain categories within \texttt{UQWorld} is limited;
 In some categories, members can't start their own topic.
@@
   \hline
+  \footnotesize{UQ Discussion Forum}        & \checkmark & \checkmark & \checkmark \\
+  \footnotesize{UQWorld Community (Meta)}   & \checkmark & \checkmark & \checkmark \\
+  \footnotesize{Features Requests}          & \checkmark & \checkmark & \checkmark \\
+  \footnotesize{Community Q\&A and How To}  & \checkmark & \checkmark & \checkmark \\   
+  \footnotesize{Case Studies}               & \checkmark & \checkmark & \checkmark \\
+  \footnotesize{Benchmarks}                 & PA         & \checkmark & \checkmark \\
+  \footnotesize{News and Announcements}     & PA         & \checkmark & \checkmark \\
+  \footnotesize{Future/Draft}               & Invisible  & \checkmark & \checkmark \\
+  \footnotesize{Developers Corner}          & \ding{55}  & PA         & \checkmark \\
+  \footnotesize{FAQ}                        & \ding{55}  & \ding{55}  & \checkmark \\
   \footnotesize{Chair's Blog}               & \ding{55}  & \ding{55}  & \checkmark \\  
-  \footnotesize{FAQ}                        & \ding{55}  & \ding{55}  & \checkmark \\
-  \footnotesize{Developers Corner}          & \ding{55}  & PA         & \checkmark \\
-  \footnotesize{Future/Draft}               & \ding{55}  & \checkmark & \checkmark \\
-  \footnotesize{News and Announcements}     & \ding{55}  & \checkmark & \checkmark \\
-  \footnotesize{Benchmarks}                 & PA         & \checkmark & \checkmark \\
-  \footnotesize{Case Studies}               & \checkmark & \checkmark & \checkmark \\
-  \footnotesize{Community Q\&A and How To}  & \checkmark & \checkmark & \checkmark \\   
-  \footnotesize{Features Requests}          & \checkmark & \checkmark & \checkmark \\
-  \footnotesize{UQWorld Community (Meta)}   & \checkmark & \checkmark & \checkmark \\
-  \footnotesize{UQ Discussion Forum}        & \checkmark & \checkmark & \checkmark \\
   \hline
@@
 
-\section{Demo}
-
 \section{What's next}
@@
 %===============================================================================
-\begin{frame}[t]{UQWorld: What's next}
+\begin{frame}[t]{What's next: A Community Cycle}
+
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}[t]{What's next?}
+
+Here's what you can do to help before UQWorld is released:
+
+\begin{enumerate}
+  \item Accept the invitation and start browse around UQWorld.
+  \item Familiarize yourself with structure and the mechanics of the platform.
+  \item Reply to the topic \emph{First time in the forum? Welcome!}
+  \item Start thinking about some of your external colleagues, how they might benefit from joining UQWorld.
+  \item Start thinking about what kind of conversation or things you want to bring or share here.
+\end{enumerate}
+
+And soon after it is released:
+
+\begin{enumerate}
+  \item For certain things, instead of sharing and discussing with the group by email, create a topic in UQWorld (but you can start early too!). 
+  \item Send personal invitation emails to your external colleagues, why they should join UQWorld (but only if you think they should).
+  \item If you still receive UQLab support email, refer the sender to UQWorld.
+  \item Regularly check UQWorld (ps: community manager will notify you separately if there's something of interest)
+\end{enumerate}
+
+\end{frame}
+%===============================================================================
+
+%===============================================================================
+\begin{frame}[t]{What to bring? An example from your inbox.}
+
+From: torre$@$ibk.baug.ethz.ch, Subject: Interesting paper
+
+\begin{quotation}
+
+ if you are interested in SVM methods for reliability analysis, this may
+ be of interest to you: ...
+
+\end{quotation}
+
+From: sudret$@$ibk.baug.ethz.ch, Subject: Re: Interesting paper
+
+\begin{quotation}
+
+  @all: I think it is generally a good practice to share links of interesting papers.
+  I do this once in a while ... In a word: feel free to send such links to the group when you find interesting papers!
+
+  ** Now, regarding that specific publication, I'm not sure it brings anything new!
+It completely ignores the work done in France on SVR for reliability since ...
+2007 by Deheeger, Bourinet, Lemaire, ...
+Moustapha (who's this guy??), And recent papers by Hurtado etc.
+  A good review should have rejected this paper for lack of novelty. AND ... I'm pretty sure our UQLab module has far more than what is presented here.
+
+  Anyway, the good news in sharing papers is that there will be always somebody in the Chair able to comment on the fact that this is interesting or not!
+\end{quotation}
 

### 2019-05-08 latex/uqworld-presentation.tex
Update slides

@@
 \end{itemize}
-%\\~\\
+
+\vspace{0.3cm}
+
 Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.
-%\\~\\
+
+\vspace{0.3cm}
+
 Besides, there seems to be an opportunity...
@@
 %===============================================================================
-\begin{frame}[t]{What's next: A Community Cycle}
+\begin{frame}[t]{What's next: An online community lifecycle}
+
+\begin{tabularx}{\textwidth}{XXXX}
+  \hline
+                                    & Inception    & Establishment  & Maturity \\
+  \hline
+  \footnotesize{Majority of members}
+  & Core members
+  & UQLab users, UQ practitioners
+  & UQ practitioners and researchers  \\
+
+  \footnotesize{Activity by comm. manager, core members}
+  & $50$\%-$100$\%
+  & $10$\%-$50$\% 
+  & $<10$\% \\
+
+  \footnotesize{Growth rate by word-of-mouth}
+  & $0$\%-$50$\% 
+  & $50$\%-$90$\%
+  & $>90$\% \\
+
+  \footnotesize{Why members join}
+  & Relationship with core members, problems with UQLab
+  & matched interests in UQ, tangible value (info, support)
+  & Tangible value: info, support, and social (incl. sharing expertise) \\
+%  \footnotesize{Example of tasks}
+%  & Define scope and goal, invite members, initiate discussions, prompt participation
+%  & Write contents (about the community), organize \emph{activities} 
+%  & off-line gatherings, manage volunteer (non core members)  \\ 
+  \hline
+\end{tabularx}
+
+\vspace{0.35cm}
+
+\emph{Critical mass}: $\geq 50\%$ activities and $\geq 50\%$ growth rate
+are by the community members themselves.
 
@@
   \item Start thinking about some of your external colleagues, how they might benefit from joining UQWorld.
+  % Benefit here means getting help, sharing expertise, or both.
   \item Start thinking about what kind of conversation or things you want to bring or share here.
@@
 \begin{enumerate}
-  \item For certain things, instead of sharing and discussing with the group by email, create a topic in UQWorld (but you can start early too!). 
-  \item Send personal invitation emails to your external colleagues, why they should join UQWorld (but only if you think they should).
+  \item For certain things, instead of sharing and discussing by email, create a topic in UQWorld (you can start early too!).  % That way we can get the conversation going.
+  \item Send personal invitations to your external colleagues, why they should join UQWorld (but only if you think they should).
   \item If you still receive UQLab support email, refer the sender to UQWorld.
-  \item Regularly check UQWorld (ps: community manager will notify you separately if there's something of interest)
+  \item Regularly check UQWorld (ps: community manager will prompt you separately if there's something of interest).
 \end{enumerate}

### 2019-05-08 latex/uqworld-presentation.tex
Update slides

@@
 
-Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.
-
+Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users\footnote{not to mention it fits this sentence: \emph{It promotes an active collaboration with research groups in ETH and in other universities in order to disseminate the good practices and associated tools for uncertainty quantification}.
+UQLab is not a pre-requisite.}.
+%in context
 \vspace{0.3cm}

### 2019-05-08 latex/uqworld-presentation.tex
Minor edit

@@
   \footnotesize{Majority of members}
-  & Core members
+  & Core members, UQLab users
   & UQLab users, UQ practitioners
@@
   \footnotesize{Why members join}
-  & Relationship with core members, problems with UQLab
+  & Direct invitation, problems with UQLab
   & matched interests in UQ, tangible value (info, support)

### 2019-05-09 latex/uqworld-presentation.tex
Minor edit

@@
 
-Some are a bit hard to read,
+Praise? Collaboration inquiry?
 \begin{itemize}
@@
   \footnotesize{Majority of members}
-  & Core members, UQLab users
+  & Core members (+invitees), UQLab users
   & UQLab users, UQ practitioners
